Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging Patterns of Queen Bumble Bees

### 2023-01-21 script/manuscript_MEE.Rmd
citations for use of alpha taxonomy literature for classing seqs

>>>>

Sequences which were assigned to genera without any species predicted by spatial analyses, were investigated by hand after post-processing steps. These were manually assigned to a variety of ranks, occasionally to genus #COUNTS# and family #COUNTS#,  by consultation of the alpha-taxonomic literature (@sadeghian2015molecular, @sennikov2017phylogenetic, @rabeler2016new, @pusalkar2015taxonomic, @moore2003its,  @weber1998new).
